\documentclass[10.5pt,letterpaper]{article}

\usepackage{hyperref, url}
\usepackage{marvosym}
\usepackage{geometry}
\usepackage{mdwlist}
\usepackage{soul}


% Fonts
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
\usepackage{url}

% Set your name here
\def\name{Sravana Reddy}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor=blue,
  pdfauthor = {\name},
  pdfkeywords = {computer science, computational linguistics, linguistics, natural language
  processing, speech recognition, machine learning, phonology, computational biology, big data, data analysis, statistics},
  pdftitle = {Curriculum Vitae},
  pdfsubject = {Sravana Reddy},
  pdfpagemode = UseNone
}

\renewcommand{\labelitemi}{$\circ$}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\small\sc}
\subsectionfont{\rmfamily\mdseries\itshape\small}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

%% Make lists without bullets and compact spacing
%\renewenvironment{itemize}{
%  \begin{list}{}{
%    \setlength{\leftmargin}{1.5em}
%    \setlength{\itemsep}{0.25em}
%    \setlength{\parskip}{0pt}
%    \setlength{\parsep}{0.25em}
%  }
%}{
%  \end{list}
%}

\begin{document}

% Place name at left
\centerline{\Large\sc \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.6\textwidth}
  Science Center\\
  Wellesley College \\
  Wellesley, MA 
 \end{minipage}
\begin{minipage}[t]{0.495\textwidth}
 \href{mailto:sravana.reddy@wellesley.edu}{sravana.reddy@wellesley.edu} \\
   \href{http://cs.wellesley.edu/~sravana/}{http://cs.wellesley.edu/~sravana/}\\ 
    (781) 985-8237
   %\href{https://github.com/sravanareddy/}{https://github.com/sravanareddy/}
 % GTalk: \href{gtalk:chat?jid=sravana.reddy@gmail.com}{sravana.reddy}\\
  %Skype: \href{skype:sravana?call}{sravana}
  
  
\end{minipage}

\section*{Research Interests}
Speech and Natural Language Processing, Machine Learning, Computational Tools for the Social Sciences.

\section*{Employment}

\begin{itemize}
\item {\bf Wellesley College}. July 2015 -- present. \\
Hess Faculty Fellow, Department of Computer Science

\item {\bf Dartmouth College}.  Sep 2012 -- June 2015.\\
Neukom Postdoctoral Fellow, Computer Science and Linguistics

\end{itemize}

\subsection*{Visiting}

\begin{itemize*}

\item Information Sciences Institute (ISI), University of Southern California. Summer 2010 \&  2011.

\item Mitsubishi Electric Research Laboratories (MERL). Summer 2009.

\item The Perseus Project, Tufts University. Summer 2006.

\item Robotics Institute, Carnegie Mellon University. Summer 2005.

\end{itemize*}

%\begin{itemize*}
%\item Research in machine translation, computer vision, dimensionality reduction, social media analysis
%\item Teaching two new, independently designed courses on computational linguistics 
%\item Advising students on research projects
%\end{itemize*}

\section*{Education}

\begin{itemize}
  \item Ph.D. in Computer Science, {\bf The University of Chicago}. Aug 2012. \\
  {\em Advisor}: John Goldsmith \\
  {\em Thesis}: Learning Pronunciations from Unlabeled Evidence
  \item M.S. in Computer Science, {\bf The University of Chicago}. Aug 2009.\\
  {\em Advisor}: John Goldsmith \\
  {\em Thesis}: Part of Speech Induction Using Non-Negative Matrix Factorization
  \item B.S. (honors) in Computer Science, Mathematics, Creative Writing,
    {\bf Brandeis University}. May 2006.
{\em Advisor}: James Pustejovsky    
\end{itemize}

\section*{Honors and Fellowships}

\begin{itemize*}
\item Neukom Fellowship, Dartmouth College, 2012-2015
\item McCormick Fellowship,  University of Chicago, 2006-2008
\item Andrew Grossbardt Memorial Prize, Brandeis University, 2006
\item DMP Fellowship, Computing Research Association, 2005
\item Academy of American Poets Prize, Brandeis University, 2004
\item Dean's List, Brandeis University, 2002-2006
\item Wien International Scholarship, Brandeis University, 2002-2006
\end{itemize*}


\section*{Grants}
%\subsection*{External}
%
%\subsection*{Internal}

\begin{itemize*}
\item Neukom CompX Grant (co-PI, \$25,000), Dartmouth College, 2015
\item Arts/Science Graduate Collaboration Grant (co-PI, \$10,000),  University of Chicago, 2012
\item Jerome Schiff Fellowship (co-PI, \$1,000), Brandeis University, 2005-2006
\item Hewlett Foundation  Grant (PI, \$400), Brandeis University, 2003
\end{itemize*}


\section*{Research}

\subsection*{Peer-Reviewed Publications}

\begin{itemize}

\item Sravana Reddy and James Stanford. \ul{Toward completely automated vowel extraction: Introducing DARLA
}. {\em Linguistics Vanguard}. 2015.

\item Sravana Reddy and James Stanford. \ul{A Web Application for Automated Dialect Analysis}. In {\em Proceedings of the Annual Conference of the North American Chapter of the Association for Computational Linguistics} (NAACL). 2015.

\item Sravana Reddy and Kevin Knight. \ul{Decoding Running Key Ciphers}. In {\itshape Proceedings of the Annual Meeting of the Association for Computational Linguistics} (ACL). 2012.

\item Sonjia Waxmonsky and Sravana Reddy. \ul{G2P Conversion of Proper Names Using Word Origin Information}. In {\itshape Proceedings of the Annual Conference of the North American Chapter of the Association for Computational Linguistics} (NAACL). 2012.

\item Sravana Reddy and Evando Gouv\^ea. \ul{Learning from Mistakes: Expanding Pronunciation Lexicons Using Word Recognition Errors}. In {\itshape Proceedings of the Annual Conference of the International Speech Communication Association} (INTERSPEECH). 2011.

\item Sravana Reddy and Kevin Knight. \ul{Unsupervised Discovery of Rhyme Schemes.} In {\itshape Proceedings of the Annual Meeting of the Association for Computational Linguistics} (ACL). 2011.

\item Sravana Reddy and Kevin Knight. \ul{What we know about the Voynich Manuscript.} In {\itshape Proceedings of the ACL LaTeCH Workshop}. 2011.

\item Sravana Reddy and John Goldsmith  \ul{An MDL-based approach to extracting subword units for grapheme-to-phoneme conversion.} In {\itshape Proceedings of the Annual Conference of the North American Chapter of the Association for Computational Linguistics} (NAACL). 2010.

\item Sravana Reddy and Sonjia Waxmonsky.  \ul{Substring-based Transliteration with Conditional Random Fields.} In {\itshape Proceedings of the ACL Named Entities Workshop}. 2010.

\item Sravana Reddy. \ul{Understanding Eggcorns}. In {\itshape Proceedings of the NAACL Workshop on Computational Approaches to Linguistic Creativity}. 2010.


\end{itemize}

%\subsection*{Under Review}
%
%\begin{itemize}
%
%%\item Sravana Reddy and James Stanford. \ul{Large-scale Twitter analysis of newly formed English clippings}. In preparation for submission to {\em American Speech}. 2015.
%
%\end{itemize}

\subsection*{Conferences (abstract-reviewed)}

\begin{itemize}
\item Sravana Reddy and James Stanford. \ul{Is the Future Almost Here? Large-Scale Completely Automated Vowel Extraction from Free Speech}. {\em New Ways of Analyzing Variation} (NWAV). 2014. 

\item Sravana Reddy, Joy Zhong, and James Stanford. \ul{A Twitter-Based Study of Newly Formed Clippings in American English}. {\em Annual Meeting of the American Dialect Society (ADS)}. 2014.

\item Sravana Reddy and Gregory Crane. \ul{A Document Recognition System for Early Modern Latin}. {\em Chicago Colloquium on Digital Humanities and Computer Science}. 2006.

\end{itemize}

\subsection*{Invited Talks}

\begin{itemize*}
\item Workshop on Automated Speech Analysis, ``Best Practices in Sociophonetics'' session at NWAV. University of Toronto, Oct 2015.
\item Automated Tools for Sociophonetic Analysis. Information Sciences Institute, Jun 2015 and Linguistic Summer Institute Workshop on Computational Phonology and Morphology, Jul 2015
\item Understanding language variation from untranscribed data. University of Vermont, Feb 2015, Wellesley College, Mar 2015, and Worcester Polytechnic Institute, Mar 2015.
\item What we know about the Voynich Manuscript. Dartmouth College, Nov 2012 and Stanford University, Mar 2013.
\item Unsupervised learning of pronunciations. BBN, Mar 2012 and University of Toronto, Oct 2011.
\item Understanding eggcorns. Information Sciences Institute, Jul 2010.
\end{itemize*}

\subsection*{Software and Data}

\begin{itemize}
\item DARLA -- Dartmouth Linguistic Automation: \url{http://darla.dartmouth.edu} (with James Stanford). System for automated analysis of phonetics from untranscribed speech.

%\item FSA Web Interface: \url{http://www.cs.dartmouth.edu/cgi-bin/cgiwrap/sravana/fsa.cgi}. Teaching tool for finite state machines.

\item Program for Unsupervised Rhyme Scheme Discovery: \url{https://github.com/sravanareddy/rhymediscovery}

\item The Chicago Rhyming Poetry Corpus: \url{https://github.com/sravanareddy/rhymedata} (with Morgan Sonderegger). Dataset of English and French poetry with rhymes annotated.
\end{itemize}

%\section*{Programming}
%\begin{itemize*}
%\item Competent: Python, R, MATLAB, JavaScript, Unix scripting, CGI, Scheme
%\item Familiar: C, C++, Java, Perl, PHP, Julia
%\end{itemize*}


\subsection*{Press}
\begin{itemize*}
\item Researchers Are Totes Studying How Ppl Shorten Words On Twitter. NPR, Jan 2014.

\item Dartmouth Hosts a Different Kind of Olympics. Dartmouth Now, Jan 2014.
\end{itemize*}

%\section*{Theses}
%
%\begin{itemize}
%\item {\bf Learning Pronunciations from Unlabeled Evidence}. Doctoral Dissertation, The University of Chicago, 2012.
%
%\item {\bf Part of Speech Induction Using Non-Negative Matrix Factorization.} Masters' Thesis, The University of Chicago, 2009.
%
%\end{itemize}

%\section*{In Progress/In Submission}
%
%\begin{itemize}
%\item {\bf Parsing page images: deciphering the Nushu script} (with Kevin Knight)
%\item {\bf Learning translation lexicons from non-parallel text using metric learning} (with Lorenzo Torresani)
%\item {\bf Characterizing visual adjectives} (with Lorenzo Torresani and Lauren Tran)
%\end{itemize}

\section*{Teaching}

\subsection*{Instructor}

\begin{itemize}
\item Natural Language Professing (Spring 2016), Wellesley College.
\item Computer Programming and Problem Solving (Fall 2015), Wellesley College.
\item Language Variation through the Lens of Web Data (July 2015), LSA Summer Institute. 
\item COSC 73: Computational Linguistics (Fall 2014 and Fall 2013), Dartmouth College. Primarily CS undergraduate and graduate course on probabilistic methods and machine learning for language.
\item LING 50: Computational Linguistics (Winter 2013), Dartmouth College. Seminar on computational and statistical methods for linguistics.
\end{itemize}

%\subsection*{Guest Lecturer}
%\begin{itemize*}
%\item Reasoning about Uncertainty (Spring 2015), UMass Amherst. {\em Random Variables}
%\item Dialectology (Spring 2014), Dartmouth College. {\em Language Variation on Social Media}
%\item Experimental Phonetics (Spring 2014), Dartmouth College. {\em Speech Recognition} and {\em Acoustics of Nasals and Fricatives}
%\item Introduction to Linguistics (Spring 2013), Dartmouth College. {\em N-Gram Language Models}
%\end{itemize*}

\subsection*{Student Advising}

\begin{itemize}
\item Emily Ahn, 2015. Statistical methods for accent recognition.
\item James Brofos (co-advised with Lorenzo Torresani), 2013. Deep learning for NLP.
\item Irene Feng, 2014. Development of website, \url{darla.dartmouth.edu}, for automated speech analysis.
\item Etai Klein, 2014. Development of an Android app, \url{https://github.com/etaiklein/Kanji-OCR}, for handwritten Kanji recognition.
\item Steven Nugent, 2013. Vector-space models for machine translation.
\item Ian Stewart (co-advised with James Stanford), 2013-2014. Papers:

\begin{itemize*}
\item \ul{African American English Syntax in Twitter}. Senior honors thesis, Dartmouth College. 2014.
\item \ul{Now We Stronger than Ever: African-American English Syntax in Twitter}. In {\em Proceedings of the EACL Student Research Workshop}. 2014.
\end{itemize*}

\item Lauren Tran (co-advised with Lorenzo Torresani), 2013. Learning translation lexicons with visual cues.

\item Crystal Ye, 2013. Native language identification.
\item Alexander Welton, 2014. Senior thesis:

\begin{itemize*}
\item \ul{StyleCheck: An Automated Stylistic Analysis Tool}. {\em Dartmouth Computer Science Technical Report TR2014-754}. 2014.
\end{itemize*}

\item Sarah Young (co-advised with James Stanford), 2014. Automated vowel analysis.
\item Joy Zhong (co-advised with James Stanford), 2013. Paper:

\begin{itemize*}
\item \ul{A Twitter-Based Study of Newly Formed Clippings in American English}. {\em Annual Meeting of the American Dialect Society (ADS)}. 2014.
\end{itemize*}
\end{itemize}

\subsection*{Lab Instructor and Teaching Assistant (University of Chicago)}

\begin{itemize*}
\item Artificial Intelligence (Winter 2012)
\item Computational Biology (Winter 2011)
\item Fundamentals of Programming (Fall 2011 lab, Winter 2008)
\item Introduction to Computer Science (Fall 2010 lab, Fall 2009 lab, Winter 2010, Winter 2009)
\item Computational Linguistics (Fall 2008)
\item Web Programming (Spring 2010 lab, Spring 2008)
\item Distributed Objects (Spring 2009)
\item Foundations of Software (Fall 2007)
\end{itemize*}

%\subsection*{Pedagogy Workshops, as participant}
%
%\begin{itemize*}
%\item Flipped Course Design (June 2013), Dartmouth Educational Technologies
%\item Teaching Methods and Practicum (Winter 2013), Dartmouth Center for the Advancement of Learning
%\item Asking the Right Questions (November 2012), Dartmouth Center for the Advancement of Learning
%\item Faculty Voice Workshop (Fall 2012), Dartmouth Center for the Advancement of Learning
%\item Seminar on Course Design  (Spring 2012), Chicago Center for Teaching
%\end{itemize*}


\section*{Service}

\begin{itemize*}

\item  Reviewer, EMNLP, NAACL, ACL, EACL, ICASSP, LSA, {\em Speech Communication} and {\em Computer Speech and Language}.

\item Co-chair, NAACL 2016 Demo Session.

\item Local Organizer, North American Computational Linguistics Olympiad (NACLO), 2013-2015. 

\end{itemize*}




%\section*{References}
%%
%\begin{itemize}

% \item John Goldsmith\\
%Edward Carson Waller Distinguished Service Professor\\
%Departments of Computer Science and Linguistics \\
%The University of Chicago\\
%1100 E. 58th Street,
%Chicago, IL 60637. \\
%773-702-6614\\
%\mbox{\small \href{mailto:goldsmith@uchicago.edu}{goldsmith@uchicago.edu}}
%
%\item Kevin Knight \\
%Senior Research Scientist and Professor \\
%Information Sciences Institute\\
%University of Southern California\\
%4676 Admiralty Way, Marina del Rey, CA 90292. \\
%310-448-8716\\
%\mbox{\small \href{mailto:knight@isi.edu}{knight@isi.edu}}
%%
%%%%\item Karen Livescu \\
%%%%Assistant Professor\\
%%%%Toyota Technological Institute at Chicago \\
%%%%6045 S. Kenwood Avenue,
%%%%Chicago, IL 60637. \\
%%%%773-834-2500,
%%%%\mbox{\small \href{mailto:klivescu@ttic.edu}{klivescu@ttic.edu}}
%%%
%%
%%%\item Lorenzo Torresani \\
%%%Assistant Professor,
%%%Department of Computer Science\\
%%%Dartmouth College,
%%%Hanover, NH 03755. \\
%%%603-646-3048,
%%%\mbox{\small \href{mailto:lorenzo@cs.dartmouth.edu}{lorenzo@cs.dartmouth.edu}}
%%
%\item James Stanford \\
%Associate Professor\\
%Program in Linguistics and Cognitive Science\\
%Dartmouth College\\
%301 Reed Hall, HB 6220, Hanover, NH 03755. \\
%603-646-0099\\
%\mbox{\small \href{mailto:james.n.stanford@dartmouth.edu}{james.n.stanford@dartmouth.edu}}

%\end{itemize}

\medskip

% Footer
%\begin{center}
%  \begin{small}
%    Last updated: \today
%  \end{small}
%\end{center}

\end{document}
